\documentclass[11pt]{article}
\usepackage{enumitem}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{fontspec}
\usepackage{fontawesome}
\usepackage{anyfontsize}
\usepackage{url}
\usepackage{geometry}
\geometry{
left=13mm,
right=13mm,
top=13mm,
bottom=16mm,
}

\setlist[2]{noitemsep}
\setlist{nosep}
\setlist[itemize]{leftmargin=*}

\textheight=10.5in
\pagestyle{empty}
%\raggedbottom
\raggedright

%  \renewcommand{\encodingdefault}{cg}
  %\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME
\newcommand{\area}[2]{\vspace*{-9pt} \begin{verse}\textbf{#1}   #2 \end{verse}  }
\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-18pt} \hrulefill \\}
\newcommand{\address}{\vspace*{-8pt} \\ \hspace*{-18pt}  \\}
\newcommand{\header}[1]{{\hspace*{-15pt}\vspace*{6pt} \textsc{#1}} \vspace*{-6pt} \lineunder }
\newcommand{\employer}[3]{{ \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }}
\newcommand{\contact}[3]{
\vspace*{-8pt}
\begin{center}
{\LARGE \scshape {#1}}\\
\vspace {3pt}
#2 \address
#3
\end{center}
\vspace*{-8pt}
}
\newenvironment{achievements}{\begin{list}{$\bullet$}{\topsep 0pt \itemsep -1.5pt \leftmargin 5pt}}{\vspace*{4pt}\end{list}}
\newcommand{\school}[4]{
 \textbf{#1} #2 $\bullet$ #3\\
#4 \\
}

% END RESUME DEFINITIONS

\begin{document}

\small
\smallskip
\vspace*{-40pt}

\begin{center}
  {\Huge \scshape {Nakul Pathak}} \\
  \vspace*{6pt}
{\fontsize{10}{1}\selectfont University of Waterloo $\cdot$ 3A Software Engineering} \\
\vspace{-4pt}
\hspace*{-18pt} \hrulefill \\
\vspace{2pt}
\hspace*{-13pt} \faPhone \  +1(226)-868-8127 \ $|$ \  \href{mailto:n4pathak@uwaterloo.ca}{\faEnvelope \ n4pathak@uwaterloo.ca} \  $|$ \  \href{http://nakulpathak.com}{\faGlobe \ nakulpathak.com}  \ $|$ \   \href{https://github.com/nakulpathak3}{\faGithub \ nakulpathak3}
\vspace{-5pt}
\end{center}

\vspace{6pt}

\header{\fontsize{11.1}{10}\selectfont Work}
\begin{achievements}

\item \textbf{{\fontsize{9.5}{10}\selectfont Growth Engineering/Identity Co-op, Shopify}} \hfill \textit {September 2016 - December 2016}

\vspace{1pt}
\item[ ] \textit{Tech Stack}: Ruby, Ruby on Rails, Coffeescript, HTML, Sass, Git.
\vspace{2pt}

\begin{itemize}
% \item[\diamond] \textbf{Tools}: Ruby, Ruby on Rails.
\item[-] Helped set up initial foundations for Identity/Single Sign On project including authentication flows following OAuth2 and Open ID Connect specifications.
\vspace{2pt}
\item[-] Reduced image load times on shopify.com by \textbf{10\%} by adding CDN tools across the application.
\vspace{2pt}
\item[-] Migrated models from storing data in YAML files to SQLite database thus allowing faster database lookups.
\end{itemize}

\vspace{5pt}

\item \textbf{{\fontsize{9.5}{10}\selectfont  Developer Operations Co-op, Oracle Eloqua}} \hfill \textit {January 2016 - April 2016}

\vspace{1pt}
\item[ ] \textit{Tech Stack}: Ruby, Bash, Vagrant, Chef, Docker, Sensu, Elasticsearch, Git.
\vspace{2pt}

\begin{itemize}
\item[-]Reduced time required to set up TeamCity agents by \textbf{63\%} by automating the set up process through Chef, Bash scripts \& Rake tasks.
\vspace{2pt}
\item[-]Reduced quarterly maintenance time from a few hours to \textbf{5 minutes} by creating Bash scripts interacting with Chef (Knife), Apache, \textbf{Sensu}, Grafana, etc. to shutdown and start up services across over 20 virtual machines.
\vspace{2pt}
\item[-]Set up an internal gem server by creating a Docker container using Geminabox gem that was deployed using Apache Mesos.
\end{itemize}

\vspace{5pt}

\item \textbf{{\fontsize{9.5}{10}\selectfont Software Developer Co-op, Payments Team, Shopify}} \hfill \textit {May 2015 - August 2015}

\vspace{1pt}
\item[ ] \textit{Tech Stack}: Ruby, Ruby on Rails, Coffeescript, HTML, Sass, Git.
\vspace{2pt}

\begin{itemize}
\item[-]Added over \textbf{100} third party payment system integrations by automating addition of these systems to Shopify. Led project from early prototype to beta phase through test-driven development.
\vspace{2pt}
\item[-]Improved financial GMV calculations by \textbf{7\%} by fixing an issue where certain payment gateways sent duplicate responses, doubling the total amount of transactions.
\vspace{2pt}
\item[-]Created and integrated \href{https://github.com/activemerchant/payment_icons}{Payment Icons} ruby gem across Shopify's codebase, providing a uniform way of adding payment icons into any Rails app. Open source on \href{https://github.com/activemerchant/payment_icons}{\textit{Github}}.
\end{itemize}
\end{achievements}

\vspace{6pt}

\header{\fontsize{11.1}{10}\selectfont Projects}
\begin{achievements}
\def\UrlFont{\em}
\item \textbf{Personal Blog Gem}  $|$  \href{https://github.com/nakulpathak3/personal-blog-gem}{\faGithub}  $|$ \href{https://rubygems.org/gems/personal_blog}{\faExternalLink} \hfill \textit {February 2016}
\begin{itemize}
\item[-]Ruby gem that adds a responsive and completely customizable personal blog with markdown support and code syntax highlighting to any Ruby on Rails application.
\vspace{2pt}
\item[-]Downloaded over \textbf{1,350} times since March 17, 2016.
\vspace{2pt}
\item[-]\textbf{Tools:} Ruby on Rails Engines, HTML, CSS, Javascript.
\end{itemize}

\vspace{5pt}

\item \textbf{One Press Man} {$|$ \scriptsize UofT HACKS 2016, \textbf{2nd Place}} $|$  \href{https://github.com/adrianmachado/Onepressman}{\faGithub} \hfill \textit {January 2016}
\begin{itemize}
\item[-]Application that uses the Pebble watch's controls as a discrete, quick panic button to message preselected contacts and 911 in emergency situations.
\vspace{2pt}
\item[-]\textbf{Tools:} C, Pebble SDK, Java.
\end{itemize}

%\vspace{3pt}2

%\item \textbf{Payment Icons Gem} {$|$ \scriptsize Open Source Contribution} $|$  \href{https://github.com/activemerchant/payment_icons}{\faGithub} \hfill \textit {August 2015}
%\begin{itemize}
%\item[-]Open source Ruby gem extracted from Shopify's code base to render various payment icons like Visa, Mastercard, etc. into any Rails application.
%\vspace{2pt}
%\item[-]Downloaded over \textbf{640} times since its release.
%\vspace{2pt}
%\item[-]\textbf{Tools:} Ruby on Rails Engines, HTML, CSS, Javascript.
%\end{itemize}

\vspace{5pt}

% DO I leave this in or the other one?
\item \textbf{Flash} {$|$ \scriptsize HACK THE NORTH 2015, Participant} $|$  \href{https://github.com/nakulpathak3/Flash}{\faGithub} \hfill \textit {September 2015}
\begin{itemize}
\item[-] Implemented an iOS application that provides users with shopping deals which expire 5 minutes after you open them.
\vspace{2pt}
\item[-] \textbf{Tools:} React Native, Braintree API, XCode.
\end{itemize}

\vspace{5pt}

\item\textbf{MyoRunner} {$|$ \scriptsize ENGHACK, \textbf{2nd Place} }  $|$  \href{https://github.com/nakulpathak3/myorunner}{\faGithub} \hfill \textit {November 2014}
\begin{itemize}
\item[-]Arm gesture controlled Temple Run type browser-based game.
\vspace{2pt}
\item[-]\textbf{Tools:} Lua and Myo SDK.
\end{itemize}

%\vspace{4pt}

%\item \textbf{Inventory Notifier App} $|$  \href{https://github.com/nakulpathak3/twilio-shopify-notifier}{\faGithub}
%\begin{itemize}
%\item[-]Web application that calls or texts Shopify merchants when their product inventory goes below 10 items.
%\item[-]\textbf{Tools:} Django (Python), Shopify API (for checking inventory), Twilio API (for calling/texting).
%\end{itemize}

%\vspace{3pt}

%\item \textbf{Feed Me!} {$|$ \scriptsize HACK THE NORTH 2014, Participant}   $|$  \href{https://github.com/nakulpathak3/FeedMe}{\faGithub} \hfill \textit {September 2014}
%\begin{itemize}
%\item[-]Web application which provides possible cooking recipes depending on ingredients searched for.
%\vspace{3pt}
%\item[-]\textbf{Tools:} Django (Python), Yummly API (for recipes).
%\end{itemize}
\end{achievements}

\vspace{6pt}

\header{\fontsize{11.1}{10}\selectfont  Education}
\begin{achievements}
\item \textbf{Bachelor of Software Engineering, University of Waterloo} \hfill \textit {September 2014 - August 2019}
\begin{itemize}
\vspace{2pt}
\item[-] Starting 3rd year (3A term) January 2017. \vspace{2pt}
\item[-] Extensively used C++ in multiple courses to learn programming concepts.
\vspace{2pt}
\item[-] Received President's Scholarship of Distinction for having admission average over 95\%.
\vspace{2pt}
\end{itemize}
\end{achievements}

\end{document}
