\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\textheight=10in
\pagestyle{empty}
%\raggedbottom
\raggedright

%  \renewcommand{\encodingdefault}{cg}
  %\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME
\newcommand{\area}[2]{\vspace*{-9pt} \begin{verse}\textbf{#1}   #2 \end{verse}  }
\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-18pt} \hrulefill \\}
\newcommand{\header}[1]{{\hspace*{-15pt}\vspace*{6pt} \textsc{#1}} \vspace*{-6pt} \lineunder}
\newcommand{\employer}[3]{{ \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }}
\newcommand{\contact}[3]{
\vspace*{-8pt}
\begin{center}
{\LARGE \scshape {#1}}\\
#2 \lineunder 
#3
\end{center}
\vspace*{-8pt}
}
\newenvironment{achievements}{\begin{list}{$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}\end{list}}
\newcommand{\schoolwithcourses}[4]{
$\bullet$
 \textbf{#1}  #2\\ 
#3   \\
\vspace*{5pt}
}
\newcommand{\school}[4]{
 \textbf{#1} #2 $\bullet$ #3\\ 
#4 \\
}
% END RESUME DEFINITIONS

\begin{document}

\small
\smallskip
\vspace*{-57pt}

\contact{Nakul Pathak}
{\normalsize MKV 304 East, University of Waterloo, Waterloo, ON, Canada N2J 4Z2}
{\normalsize(226) 868-8127  \hfill n4pathak@uwaterloo.ca   \hfill www.nakulpathak.com}
{
\vspace{10pt}
\header{Education}

\schoolwithcourses{University of Waterloo, 1st Year(1A Term)}{Waterloo, Ontario, Canada.}{Bachelor of Software Engineering Honours Co-op, 2014-2019}
{}
\schoolwithcourses{DPS RK Puram}{New Delhi, India}{Graduated with 96\% average in Physics, Chemistry, Mathematics and Computer Science(99\%)}

\vspace{7pt}

\header{Technical Skills}
\begin{achievements}
\item Learned \textbf{HTML/CSS, JavaScript, AngularJS, jQuery, jQuery UI, LaTeX} through online courses (Codecademy, CodeSchool, Youtube Tutorials).
\item 3 years experience coding in \textbf{C++}
\item Proficient in \textbf{SQL, GQL} database queries.
\item Learned \textbf{Python, Lua, Google App Engine} through Udacity Course and online tutorials.
\item Currently learning \textbf{AJAX requests} through Udacity Online Course
\item Experience with \textbf{Git, Github, Bash}. Used \textbf{Bind9} to set up DNS server for personal website. (Saved money by not using cloud hosting services)
\end{achievements}

\vspace{7pt}

\header{Professional Skills}
\begin{achievements}
\item Extensive self-learner with inherent curious attitude and desire to learn  
\item Passion for problem solving 
\item Excellent communication and leadership skills developed through position as chief editor of school magazine for 2 years
\end{achievements}

\vspace{7pt}

\header{Projects and Work Experience}
\begin{achievements}
\item \textbf{Built blog from scratch} \hfill \textit {Current}
\\ Built a blog using Python and Google App Engine which utilizes HTTP Requests, Form Handling and GQL, and then integrated this with my website. Now, expanding this into a full-fledged blogging service with user authentication, password and cookie hashing
\item\textbf{MyoRunner}\hfill\textit{2nd November, 2014}
\\ Won 2nd prize at EngHack by building a Temple-Run like browser based web game. Learned Lua scripting to program Myo for playing the game through gestures. 
\item \textbf{Feed Me!} \hfill \textit {September 2014}
\\ A web app which provides possible recipes you can make with the ingredients you list in a search by parsing the ingredients across an API from Yummly. Uses Django and Python. Built at Hack The North.
\item \textbf{Designed Online Portfolio} \hfill \textit {June - July 2014}
\\ Used self taught skills in web development to make personal website. Further strengthened web development skills through application of skills I learned.
\item \textbf{SAT Tutor} \hfill \textit {April - July 2014}
\\ After securing 99th percentile scores in all sections of the SAT, I tutored students over the summer explaining and discussing concepts ranging from english to complex math problems.
\end{achievements}

\vspace{7pt}

\header{Standardized Tests}
\begin{achievements}
\item SAT Score- 2360/2400 \hfill \textit {December 2013}
    \setlength\itemsep{0.03em}
     \vspace{-1.5ex}\\
     \begin{itemize}
     \setlength\itemsep{0.03em}
        \item Math- 790/800
        \item Critical Reading- 770/800
        \item Writing- 800/800
    \end{itemize}
\vspace{-1ex}
\item TOEFL- 113/120 \hfill \textit {December 2013}
\vspace{-0.4ex}
\item SAT Math Level II - 780/800 \hfill \textit {January 2014}
\end{achievements}

\vspace{7pt}

\header{Co-Curricular Activities}
\begin{achievements}
\item \textbf{HH Internships/Co-op Group Creator and Admin} \hfill \textit {November 2014- Current}
\\ Created a subgroup of Hackathon Hackers for students to matchup with startups/big companies/other students for internships as well as to help each other with academics, resumes, advice, etc.
\item \textbf{Engineering Ambassador, University of Waterloo} \hfill \textit {September 2014- Current}
\\Keep up online presence for future students who can contact me for shadow days, general questions. Also, involved with various activities that Ambassador program holds.
\item \textbf{Youreka Adventure Camp Champion} \hfill \textit {June 2012}
\\ Awarded Youreka adventure camp champion award for excellent leadership and communication skills. Also awarded role model stamp. Participated in white water rafting, river crossing, cliff diving, etc.
\end{achievements}

\newpage

\ In 10th grade, I watched The Social Network. As I watched Mark Zuckerberg, swiftly hack all of Harvard's directories and use "some wget magic" to extract pictures from them, I felt the fire in my heart. The passion began to arise. I fell in love with the sound of the keystrokes, the computer following the maestro's commands and making magic happen. I watched him create a product, from his dorm room, a product now used by 7 billion people. Just an idea, translated into code and that code created Facebook. He held the power to type commands, write logic and create things that connected the entire world. He did that from his dorm room sitting in front of a computer. The device in front of me is the most powerful thing created by humanity. I hold the power as a coder to create magic. The day after Zuckerberg inspired me, the curiosity began to develop. I needed to know more. My curious mind developed a thirst. I googled how to start programming. I got to know that C/C++ are excellent languages for students to start off with. A week later, I was enrolled in a course at a company. I learned C/C++ during the summer of grade 10. I felt the passion dwindling as the teacher gave boring lessons and told me to make stars on the screen. I still picked to learn programming in both grade 11 and 12 hoping something better would come off it. I learned sorting, algorithms, file handling, big O notation but that feeling that watching Zuckerberg rattle his fingers on the keyboard produced in me was forgotten.
The summer after grade 12, I had been admitted to the University of Waterloo with a 96\% average in high school. I had free time as my exams had finished by April and University didn't start till late August. I googled the same thing I had googled two years ago. I reached CodeAcademy. As I powered through the lessons, I felt that curiousity, that passion to constantly learn more rise again. I was Zuckerberg. I was the guy making magic happen. I felt powerful again. The excitement was back. I learned as much as I could everyday, day in day out. I was addicted. I finished HTML/CSS, Javascript, Jquery, Jquery UI on Codecademy  and then moved onto Dash and then to CodeSchool and then to Youtube tutorials and then to Coursera. The desire to learn everything was burning inside and no matter how much I learned, my thirst wasn't quenched. After this, I started building my website. Two months of labour went into building the website. I loved every moment of it. StackOverflow was my new best friend. I came to Waterloo and participated in Hack The North. Initially, I was just keeping up with university courses. As I learned better time management, I started on the online courses journey again. Now, it was Udacity. I had trouble balancing both things but the desire to learn was too strong for me to stop. I finished Introduction to Web Development and again, used what I had learned to shift my website to Google App Engine. I made projects as part of the course. I was doing magic again. I was the wizard again. I know I will continue to be a magician for a long long time. I need to learn more and more spells, until I am powerful enough to make beautiful magic happen at blazing speeds. I know the journey will be long but I am never stopping. I continue to learn more and more everyday. 

\end{document}