\documentclass[10pt]{article}
\usepackage{enumitem}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage{anyfontsize}
\usepackage{url}
\usepackage{geometry}
\geometry{
left=13mm,
right=13mm,
top=19mm,
bottom=19mm,
}

\setlist[2]{noitemsep}
\setlist{nosep}
\setlist[itemize]{leftmargin=*}

\textheight=10.5in
\pagestyle{empty}
%\raggedbottom
\raggedright

%  \renewcommand{\encodingdefault}{cg}
  %\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME
\newcommand{\area}[2]{\vspace*{-9pt} \begin{verse}\textbf{#1}   #2 \end{verse}  }
\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-18pt} \hrulefill \\}
\newcommand{\address}{\vspace*{-8pt} \\ \hspace*{-18pt}  \\}
\newcommand{\header}[1]{{\hspace*{-15pt}\vspace*{6pt} \textsc{#1}} \vspace*{-6pt} \lineunder }
\newcommand{\employer}[3]{{ \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }}
\newcommand{\contact}[3]{
\vspace*{-8pt}
\begin{center}
{\LARGE \scshape {#1}}\\
\vspace {3pt}
#2 \address
#3
\end{center}
\vspace*{-8pt}
}
\newenvironment{achievements}{\begin{list}{$\bullet$}{\topsep 0pt \itemsep -1.5pt \leftmargin 5pt}}{\vspace*{4pt}\end{list}}
\newcommand{\school}[4]{
 \textbf{#1} #2 $\bullet$ #3\\ 
#4 \\
}

% END RESUME DEFINITIONS

\begin{document}

\small
\smallskip
\vspace*{-45pt}

\begin{center}
	{\Huge \scshape {Nakul Pathak}} \\
	\vspace*{6pt} 
{\fontsize{10}{1}\selectfont University of Waterloo $\cdot$ Software Engineering} \\
\vspace{-4pt}
\hspace*{-18pt} \hrulefill \\
\vspace{2pt}
\hspace*{-18pt} (226)-868-8127 $|$ n4pathak@uwaterloo.ca $|$ \urlstyle{same}\url{http://nakulpathak.com} $|$  \urlstyle{same}\url{http://github.com/nakulpathak3}
\vspace{-5pt}
\end{center}

\vspace{8pt}

\header{\fontsize{11}{12}\selectfont Technical Skills}
\begin{achievements}
\item \textbf{Languages}: Ruby, Python, Javascript, C++, Swift, HTML, CSS, Assembly.
\item \textbf{Frameworks}: Ruby on Rails, Flask, Django, Node.js, React Native, jQuery, Bootstrap.
\item \textbf{Tools}: Git, Bash.
\item \textbf{Databases}: MySQL, PostgreSQL, SQLite, SQLAlchemy (ORM).
\item \textbf{Miscellaneous}: RESTful API development, Unix based systems, Algorithms \& design patterns.
\end{achievements}

\vspace{8pt}

\header{\fontsize{11}{12}\selectfont  Work Experience}
\begin{achievements}
\item \textbf{Developer Intern, Payments Team, Shopify} \hfill \textit {May 2015 - August 2015}
\begin{itemize}
\item[-]Added over 20 third party payment system integrations by automating addition of these systems to Shopify. Led project from early prototype to beta phase through test-driven full-stack web development work.
\vspace{2pt}
\item[-]Improved financial GMV calculations by 10\% by fixing long-standing issue where payment gateways sent duplicate responses, doubling total amount of transactions. 
\vspace{2pt}
\item[-]Independently created, open-sourced, and integrated Payment Icons ruby gem across Shopify's codebase, providing a simple and uniform way of adding these icons into any Rails app.
\vspace{2pt}
\item[-]Deployed Shopify's codebase to production over 15 times and made over 30 pull requests, helping various teams including data, shipping, and security.
\end{itemize}
\end{achievements}

\vspace{8pt}

\header{\fontsize{11}{12}\selectfont Relevant Projects}
\begin{achievements}
\def\UrlFont{\em}
\item \textbf{Flash} {$|$ \scriptsize HACK THE NORTH 2015, Participant} $|$  \href{https://github.com/nakulpathak3/Flash}{\faGithub} \hfill \textit {September 2015}
\begin{itemize}
\item[-]Implemented an iOS application that provides users with deals which expire 5 minutes after opening.
\item[-]Currently building a Node.js + Express application that allows Shopify merchants to post deals and receive payments.
\end{itemize}
\vspace{2pt}
\item \textbf{Payment Icons Gem} $|$  \href{https://github.com/activemerchant/payment_icons}{\faGithub} \hfill \textit {August 2015}
\begin{itemize}
\item[-]Extracted Shopify's payment icons into an open-source gem currently used by over 175 3rd-party developers.
\item[-]Ruby on Rails engine, which mounts payment icon assets and frozen record model to access those assets, into any rails app.
\end{itemize}
\vspace{2pt}
\item \textbf{Inventory Notifier App} $|$  \href{https://github.com/nakulpathak3/twilio-shopify-notifier}{\faGithub} \hfill \textit {February 2015}
\begin{itemize}
\item[-]Used Django and Twilio API to build web application that calls or texts Shopify merchants when their product inventory goes below 10 items.
\end{itemize}
\vspace{2pt}
\item \textbf{Library Management API} $|$  \href{https://github.com/nakulpathak3/books-api-rails}{\faGithub}  \hfill \textit {February 2015}
\begin{itemize}
\item[-]Created RESTful API for managing books using Ruby on Rails \& CRUD methodology.
\item[-]Utilized best practices such as versioning, namespacing, etc.
\end{itemize}
\vspace{2pt}
\item \textbf{Blogging Service} $|$  \href{https://github.com/nakulpathak3/flask-tutorial}{\faGithub} \hfill \textit {December 2014}
\begin{itemize}
\item[-]Built a blogging service which includes OAuth authentication login, user profiles, following users, etc. using Flask.
\end{itemize}
\vspace{2pt}
\item \textbf{To-Do List API} $|$  \href{https://github.com/nakulpathak3/flask-rest-api}{\faGithub} \hfill \textit {December 2014}
\begin{itemize}
\item[-]Learned REST principles and Flask by building API for managing to-do list through HTTP requests.
\end{itemize}
\vspace{2pt}
\item\textbf{MyoRunner} {$|$ \scriptsize ENGHACK, 2nd Place }  $|$  \href{https://github.com/nakulpathak3/myorunner}{\faGithub} \hfill \textit {November 2014}
\begin{itemize}
\item[-]Developed arm gesture controlled Temple Run type browser-based game using Lua and Myo SDK.
\end{itemize}
\vspace{2pt}
\item \textbf{Feed Me!} {$|$ \scriptsize HACK THE NORTH 2014, Participant}   $|$  \href{https://github.com/nakulpathak3/FeedMe}{\faGithub} \hfill \textit {September 2014}
\begin{itemize}
\item[-]Created a Django web application which provides possible cooking recipes by parsing ingredients listed in a search across an API from Yummly.
\end{itemize}
\end{achievements}

\vspace{8pt}

\header{\fontsize{11}{12}\selectfont Extracurricular Activities \& Achievements}
\begin{achievements}
\item \textbf{Software Engineering Orientation Leader} \hfill \textit {September 2015}
\begin{itemize}
\item[-] Led orientation group throughout week, set up events, guided students across different events, and answered questions about university life.
\end{itemize}
\vspace{2pt}
\item \textbf{Engineering Ambassador, University of Waterloo} \hfill \textit {September 2014- Current}
\begin{itemize}
\item[-] Represented University of Waterloo by creating online portfolio. Actively participated in events like move-ins, shadow days.
\end{itemize}
\vspace{2pt}
\item \textbf{HH Internships/Co-op Group Creator and Admin} \hfill \textit {November 2014- Current}
\begin{itemize}
\item[-]Created a group, with over 1100 members, for students to match up with companies for internships \& to help each other with academics, resumes, advice, etc.
\end{itemize}
\vspace{2pt}
\item \textbf{Standardized Tests} \hfill \textit {December 2013}
\begin{itemize}
\item[-]SAT - 2360 (99th percentile), SAT Math Level II - 780, TOEFL - 113.
\end{itemize}
\end{achievements}

\end{document}