\documentclass[10pt]{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{anyfontsize}
\usepackage{url}
\usepackage[margin=1.77800cm ]{geometry}
\textheight=10in
\pagestyle{empty}
%\raggedbottom
\raggedright

%  \renewcommand{\encodingdefault}{cg}
  %\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME
\newcommand{\area}[2]{\vspace*{-9pt} \begin{verse}\textbf{#1}   #2 \end{verse}  }
\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-18pt} \hrulefill \\}
\newcommand{\address}{\vspace*{-8pt} \\ \hspace*{-18pt}  \\}
\newcommand{\header}[1]{{\hspace*{-15pt}\vspace*{6pt} \textsc{#1}} \vspace*{-6pt} \lineunder}
\newcommand{\employer}[3]{{ \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }}
\newcommand{\contact}[3]{
\vspace*{-8pt}
\begin{center}
{\LARGE \scshape {#1}}\\
\vspace {3pt}
#2 \address
#3
\end{center}
\vspace*{-8pt}
}
\newenvironment{achievements}{\begin{list}{$\bullet$}{\topsep 0pt \itemsep -1.5pt \leftmargin 5pt}}{\vspace*{4pt}\end{list}}
\newcommand{\school}[4]{
 \textbf{#1} #2 $\bullet$ #3\\ 
#4 \\
}
% END RESUME DEFINITIONS

\begin{document}

\small
\smallskip
\vspace*{-45pt}

\begin{center}
	{\Huge \scshape {Nakul Pathak}} \\
\vspace*{6pt} 
{\fontsize{10}{1}\selectfont University of Waterloo $\cdot$ 1B Software Engineering} \\
\vspace{-4pt}
\hspace*{-18pt} \hrulefill \\
\vspace{2pt}
\hspace*{-18pt} (226)-868-8127 $|$ n4pathak@uwaterloo.ca $|$ \urlstyle{same}\url{http://nakulpathak.com} $|$  \urlstyle{same}\url{http://github.com/nakulpathak3}
\vspace{-5pt}
\end{center}


\vspace{5pt}
\header{\normalsize Technical Skills}
\begin{achievements}
\item \textbf{Languages}: C, C++, Python, Ruby, Javascript
\item \textbf{Markup Languages}: HTML, XML, LaTeX
\item \textbf{Tools}: Flask, Rails, jQuery, Google App Engine, Bootstrap, Git, Bash
\item \textbf{Databases}: MySQL, Oracle SQL/PLSQL
\end{achievements}

\vspace{5pt}

\header{\normalsize Relevant Projects}
\begin{achievements}
\def\UrlFont{\em}
\item \textbf{Ruby on Rails API} \hfill \textit {Current}
\\ Further learning Rails, after completing Rails For Zombies course, by building RESTful API service through online tutorial.
\item \textbf{Blogging Service} $|$ \url{http://nakul-microblog.herokuapp.com} \hfill \textit {December 2014}
\\ Built a blogging service using Flask and Python. Features include OAuth authentication login, user profiles, following users, writing posts, etc. Pagination, unit testing also included.
\item \textbf{Flask Todo API}  \hfill \textit {December 2014}
\\ Made secure, RESTful Flask API which uses HTTP requests to perform tasks on a to do list.
\item \textbf{Online Portfolio} $|$  \url{http://nakulpathak.com} \hfill \textit {December 2014}
\\ Made personal website after learning HTML, CSS, jQuery, Bootstrap.
\item \textbf{ASCII Chan}  $|$ \url{http://nakul-asciichan.appspot.com} \hfill \textit {November 2014}
\\ Created ASCII Art Service using Python and App Engine as part of Udacity course. Uses Google Maps API, HostIP API, App Engine Datastore. Also, includes caching to reduce requests to database. 
\item\textbf{MyoRunner}  {$|$ \scriptsize ENGHACK, 2nd Place $|$ }  \url{http://jhudson.ca/myorunaway/}\hfill \textit {November 2014}
\\ Learned Lua to create temple run type browser based game controlled by Myo.
\item \textbf{Feed Me!} {$|$ \scriptsize HACK THE NORTH, Participant}  \hfill \textit {September 2014}
\\ Used Django and Python to create a web app which provides possible recipes to make with ingredients listed in a search by parsing an API from Yummly.
\item \textbf{Online Courses} $|$ \url{https://www.udacity.com/course/cs253} \hfill \textit {September 2014}
\\ Introduction To Web Development - Python Basics $\cdot$ HTTP Requests  $\cdot$ Form Handling $\cdot$ Cookie \& Password Hashing $\cdot$ APIs $\cdot$ Caching $\cdot$ Scaling Up
\item \textbf{Pick The Odd Image Out} $|$ \url{http://picktheoddimageout.bitballoon.com} \hfill \textit{August 2014}
\\ Currently in progress. Built image version of pick the odd one out using Angular.JS. 
\end{achievements}

\vspace{5pt}

\header{\normalsize Awards, Scholarships \& Achievements}
\begin{achievements}
\item \textbf{Standardized Tests} \hfill \textit {December 2013}
\\ SAT - 2360, SAT Math Level II - 780, TOEFL - 113 
\item \textbf{President's Scholarship of Distinction} \hfill \textit {September 2014}
\\ Scholarship given by University of Waterloo for achieving 96\% in grade 12 and 99\% in Computer Science.
\item \textbf{International Experience \& Research Awards} \hfill \textit {September 2014}
\\ Scholarships by University of Waterloo for academic and co-curricular excellence, usable in upper years for international co-ops and research opportunities
\end{achievements}

\vspace{5pt}

\header{\normalsize Co-curricular Activities}
\begin{achievements}
\item \textbf{Engineering Ambassador, University of Waterloo} \hfill \textit {September 2014- Current}
\\ Represented University of Waterloo by creating online portfolio. Actively participated in events like shadow days.
\item \textbf{HH Internships/Co-op Group Creator and Admin} \hfill \textit {November 2014- Current}
\\ Created a group for students to match up with startups/big companies/other students for internships \& to help each other with academics, resumes, advice, etc. Currently has 746 members.
\item \textbf{Chief Editor, School Magazine, DPS RK Puram} \hfill \textit {December 2012- March 2014}
\\ Lead team, delegated tasks, decided which articles to add, edited articles, contacted teachers and external agencies for magazine content and design.
\end{achievements}

\vspace{5pt}

\header{\normalsize Volunteer Experience}
\begin{achievements}
\item \textbf{Juhu Angels Welfare Association}   \hfill \textit{May 2013}
\\ Removed 5 tonnes of litter from beach in Mumbai. Educated visitors about beach cleanliness through campaigns.
\item \textbf{Savera NGO}     \hfill \textit{August 2012}
\\ Created educational posters, made seating arrangements, registered student background profiles, etc. for health checkup camps in 8 Delhi schools.
\item \textbf{ISS Facility Services}    \hfill \textit{June 2011}
\\ Trained unemployed youth to help them gain employment through basic English usage, hygiene, etiquettes and grooming at slums in East Delhi.
\end{achievements}

\end{document}